Simulations of Ballot Polling Risk-Limiting Audits

### 2023-02-13 providence/sections/adversary.tex
theoretical properties section

\subsection{Efficiency}
\begin{lemma}
\label{lem:efficiency}
% For any round schedule %$[n_1, \ldots, n_r]$
For any risk-limit $\alpha \in (0, 1)$, for any margin
and for any round schedule $[n_1, \ldots, n_j]$, 
the \Providence RLA stops before or in the same round as EoR \BRAVO.
\end{lemma}
\begin{proof} Appendix~\ref{sec:proofs}\end{proof}

>>>>

\subsection{Theoretical Properties}
Here we briefly give two interesting theoretical properties of \Providence.

\subsubsection{Efficiency}
In terms of expected ballots sampled, it is easy to see that \Providence dominates EoR \BRAVO in the sense that for any sample for which the EoR \BRAVO stopping condition is met, the \Providence stopping condition is met also.
\begin{lemma}
\label{lem:efficiency}
% For any round schedule %$[n_1, \ldots, n_r]$
For any risk-limit $\alpha \in (0, 1)$, for any margin
and for any round schedule $[n_1, \ldots, n_j]$, 
the \Providence RLA stops before or in the same round as EoR \BRAVO.
\end{lemma}
\begin{proof} Appendix~\ref{sec:proofs}\end{proof}

\subsubsection{Markov-like Stopping Condition}
After $j-1$ rounds, having drawn $n_{j-1}$ cumulative ballots with $k_{j-1}$ cumulative winner ballots, the \Providence stopping condition in round $j$ with size $n_j$ is equivalent to the \Providence stopping condition for a second round where the first round size is $n_1=n_{j-1}$ with $k_1=k_{j-1}$ winner ballots and a second round size $n_2=n_j$. The particular sequence of round sizes and winner ballots found does not affect the \Providence stopping condition; only the previous cumulative round size and number of winner ballots matters. \Minerva does not have this property, but \BRAVO also does.

\begin{lemma}\label{lemma:markov}
Let $[n_1, \ldots, n_{j-1}, n_j]$ be a round schedule for an execution of \Providence audit that has not stopped
in any of its first $j-1$ rounds (\textit{i.e.,} for every $i = 1, \ldots, j-1$:
$k_i < k^{p_a, p_0, \alpha, k_{j-1}}_{min, j, n_{j-1}, n_j} $), then:

\[ 
k^{p_a, p_0, \alpha, k_{j-1}}_{min, j, n_{j-1}, n_j} = k^{p_a, p_0, \alpha, k_{j-1}}_{min, 2, n_{j-1}, n_j} .
\]
\end{lemma}
\begin{proof}
Appendix~\ref{sec:proofs}
\end{proof}

### 2023-02-13 providence/sections/appendix.tex
theoretical properties section

\begin{lemma}
    \label{lemma:sigma_increasing}
For $0<p_0< p_a< 1$ and $n>0$, the ratio $\sigma(k,p_a,p_0,n)$ is strictly increasing as a function of $k$ for $0\le k\le n$.
\end{lemma}
\begin{proof}
See \cite[Lemma 4]{usenix_minerva}. 
\end{proof}

@@

\begin{lemma}\label{lemma:markov}
Let $[n_1, \ldots, n_{j-1}, n_j]$ be a round schedule for an execution of  \Providence audit that has not stopped
in any of its first $j-1$ rounds (\textit{i.e.,} for every $i = 1, \ldots, j-1$:
$k_i < k^{p_a, p_0, \alpha, k_{j-1}}_{min, j, n_{j-1}, n_j} $), then:

\[ 
k^{p_a, p_0, \alpha, k_{j-1}}_{min, j, n_{j-1}, n_j} = k^{p_a, p_0, \alpha, k_{j-1}}_{min, 2, n_{j-1}, n_j} .
\]
\end{lemma}
% \fpo{this can be used to prove that \Providence is more efficient than \Minerva and \BRAVO}
\begin{proof}
Let $k_{j-1}$ denote the number of ballots drawn for the declared winner up to the round $j-1$ (out of $n_{j-1}$ sampled ballots). The stopping decision for the round $j$ is made as follows:

@@

\efficiencylemma

% 
% Now, if we consider $k^* = k^{p_a, p_0, \alpha}_{min, \BRAVO, n_r}$ then it is easy to see that:
% 
% 
\end{proof}

>>>>

\textbf{Lemma \ref{lem:efficiency}.}
For any risk-limit $\alpha \in (0, 1)$, for any margin
and for any round schedule $[n_1, \ldots, n_j]$, 
the \Providence RLA is more efficient than EoR \BRAVO.

% 
% Now, if we consider $k^* = k^{p_a, p_0, \alpha}_{min, \BRAVO, n_r}$ then it is easy to see that:
% 
% 
\end{proof}
\begin{lemma}
    \label{lemma:sigma_increasing}
For $0<p_0< p_a< 1$ and $n>0$, the ratio $\sigma(k,p_a,p_0,n)$ is strictly increasing as a function of $k$ for $0\le k\le n$.
\end{lemma}
\begin{proof}
See \cite[Lemma 4]{usenix_minerva}. 
\end{proof}

@@

\textbf{Lemma \ref{lemma:markov}.}
Let $[n_1, \ldots, n_{j-1}, n_j]$ be a round schedule for an execution of  \Providence audit that has not stopped
in any of its first $j-1$ rounds (\textit{i.e.,} for every $i = 1, \ldots, j-1$:
$k_i < k^{p_a, p_0, \alpha, k_{j-1}}_{min, j, n_{j-1}, n_j} $), then:

\[ 
k^{p_a, p_0, \alpha, k_{j-1}}_{min, j, n_{j-1}, n_j} = k^{p_a, p_0, \alpha, k_{j-1}}_{min, 2, n_{j-1}, n_j} .
\]
% \fpo{this can be used to prove that \Providence is more efficient than \Minerva and \BRAVO}
\begin{proof}
Let $k_{j-1}$ denote the number of ballots drawn for the declared winner up to the round $j-1$ (out of $n_{j-1}$ sampled ballots). The stopping decision for the round $j$ is made as follows:

@@
